---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 150
)
```

# KMunicate

<!-- badges: start -->
<!-- badges: end -->

The goal of {KMunicate} is to produce Kaplan–Meier plots in the style recommended following the [KMunicate study](http://dx.doi.org/10.1136/bmjopen-2019-030215) (TP Morris *et al*. Proposals on Kaplan–Meier plots in medical research and a survey of stakeholder views: KMunicate. *BMJ Open*, 2019, 9:e030215). 

## Installation

You can install {KMunicate} from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ellessenne/KMunicate-package")
```

## Example

```{r packages}
library(survival)
library(KMunicate)
```

The {KMunicate} package comes with a couple of bundled dataset, `cancer` and `brcancer`.
The main function is named `KMunicate`:

```{r brcancer, fig.height = 7, fig.width = 7 / sqrt(2)}
KM <- survfit(Surv(rectime, censrec) ~ hormon, data = brcancer)
time_scale <- seq(0, max(brcancer$rectime), by = 365)
KMunicate(fit = KM, time_scale = time_scale)
```

```{r cancer, fig.height = 7, fig.width = 7 / sqrt(2)}
KM <- survfit(Surv(studytime, died) ~ drug, data = cancer)
time_scale <- seq(0, max(cancer$studytime), by = 7)
KMunicate(fit = KM, time_scale = time_scale)
```
